Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-05-22 paper/manuscript.Rmd
End float package is not compatible with em-dashes in the captions.

```{r fig-pca, fig.width=3.57, fig.height=6.65, out.width="3.57in", out.height="6.65in",  out.extra="center", fig.cap="The flexibility of plant strategies. (a) The two first components explain a large proportion of the total variance. (b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points—which represent the strategy (the particular combination of ecological factors) of that species in its community—do not seem to be grouped by plant species. (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species. Only two of the examined species had strategies that were less flexible than would be expected at random."}
height0 <- 1.55
height1 <- 2.7
height2 <- 2.4
strategy_fig_height <- sum(height0, height1, height2)
# fig_pca <- plot_pca(pcas, chosen_threshold = 0)
# fig_distances <- plot_permanova_dist(permanova_plant_distances, permanova_site_distances)
# fig_pca_contrib <- plot_pca_variances_and_contributions(pcas, chosen_threshold = 0)
# pdf(width = 3.57, height = strategy_fig_height)
drake::loadd(fig_pca_contrib)
drake::loadd(fig_pca)
drake::loadd(fig_distances)
cowplot::plot_grid(
  fig_pca_contrib,
  fig_pca,
  fig_distances,
  ncol = 1, 
  rel_heights = c(height0, height1, height2), 
  align = "v"
)
# dev.off()
```

>>>>

```{r fig-pca, fig.width=3.57, fig.height=6.65, out.width="3.57in", out.height="6.65in",  out.extra="center", fig.cap="The flexibility of plant strategies. (a) The two first components explain a large proportion of the total variance. (b) When plants that were sampled in more than one community are plotted in terms of these two components, we observe that their points, which represent the strategy (the particular combination of ecological factors) of that species in its community, do not seem to be grouped by plant species. (c) This was confirmed using Monte Carlo randomizations of the median distance between strategies of a plant species. Only two of the examined species had strategies that were less flexible than would be expected at random."}
height0 <- 1.55
height1 <- 2.7
height2 <- 2.4
strategy_fig_height <- sum(height0, height1, height2)
# fig_pca <- plot_pca(pcas, chosen_threshold = 0)
# fig_distances <- plot_permanova_dist(permanova_plant_distances, permanova_site_distances)
# fig_pca_contrib <- plot_pca_variances_and_contributions(pcas, chosen_threshold = 0)
# pdf(width = 3.57, height = strategy_fig_height)
drake::loadd(fig_pca_contrib)
drake::loadd(fig_pca)
drake::loadd(fig_distances)
cowplot::plot_grid(
  fig_pca_contrib,
  fig_pca,
  fig_distances,
  ncol = 1, 
  rel_heights = c(height0, height1, height2), 
  align = "v"
)
# dev.off()
```
